\chapter{Background}

\large  The internet and computers have played significant role in a transformation of documents. Before documents got digitized, it used to be in form of printed papers. Most of the documents have their own layouts which is highly dependent on the language since the language comes with its own grammatical rules and the way of sentence formation. Once the smartphone came into the world, it started influencing the way of documents being prepared. To understand the text document has always been a part of interest in computer science. Since the impact of having a system that can understand the text document correctly, its repeatable functionality and speed that could help industries or companies to bring down the cost and time they are spending on dealing with documents on their day to day life. However, there are many steps in between to address before machine can read and understand text and layout information in text documents. Start with the letters, words and sentences. These are the basic and prime components of any language. One can not pass any information without it. One can argue about passing information in terms of symbol or a figure but at the basic level a letter is like a symbol or a figure that represents some value or information. We as a human being can easily recognise the texture and the layout of the letter by just looking at it, which is not the case for computers. Till the date computers are using 1s and 0s to perform tasks. Therefore it is a challenge to be able to recognise and process the letters that have been used in word or sentence while generating the document and form a structure of 1s and 0s so that machine can understand. 

\input{chapters/Background/Compilers}

\input{chapters/Background/OCR}

\input{chapters/Background/Machine_Translation}

\input{chapters/Background/Transformer}

\input{chapters/Background/Pre-Training and Fine-Tunning}

\input{chapters/Background/Cloud_Computing}





