\section{Machine Translation}

OCR provides ability to extract the letters out of documents and compilers can translate the specific language structure in a way that machine can understand, However, there is some mechanism missing between compiling High-language programming language and understanding the letters, words or sentences derived from parsing the document. Language plays a dominant role in terms of passing information, thoughts and ideas. In addition, different regions, countries and part of the world have different languages that varies in structure, grammar, letters and so on making it difficult to come with the logic or mathematical rule which can apply on one or more languages in order to understand for machines. The early approach of Noam Chomsky \cite{robert1957review}, who introduced syntactic structures as a formalized theory of linguistic structure. He introduced rules based on universal grammar, However languages are generally not well-defined and lack in stable structure hence the approach had several drawbacks. Although, the approach was not perfect, it started the true evolution of NLP. Later on the trend shifted to using probabilities and statistics for machine translation but the progress of slower than expected resulting in less funding. It was the year 1969, Roger Schank presented the concept of using tokens \cite{tokenization_history} which is still being used in NLP, Tokens provided better grasp to map sentences, it can provide better insights to machine with detailed information at object-level. 

In the 1980's, an emerging field of computer science, Machine Learning was progressing significantly in the domain of computing. Algorithms like decision trees provide enough confidence for machine to take decision using if-then rules provided acceptable evidence and new ways to conceptualise the language rather then using handwritten rules. Currently, the trend has been changed to neural networks or deep-learning. Deep-learning became the most efficient way to deal with natural languages since it is not necessary for a programmer to provide rules to decide, algorithm improves the accuracy or efficiency by mapping an input to an output and reducing the errors. 