\chapter{Introduction}

\section{Motivation}

\large We all had heard the term "Document". It has many forms for instance handwritten text, PDFs, scans, images, memos, legal prescriptions, emails, screenshots, forms and many more. With different regions and countries, it differs in languages and layouts. Documents has played a crucial role in Globalization, especially in industries, since companies should have well translated documentation of their products or services in order to be successful in international market. Usually, products and services have more than one user group, e.g. administrators, users and developers. Similar to a Language, Documents serves the key purpose of transferring information. As a Language is wide and complex field, dealing with text-documents can cost companies time and money. Many different approaches has been used to address with multi-lingual documents, the early approach of \acrlong{nlp} was "\acrlong{mt}". The interest of term machine translation is increasing among firms, Since, they may have to outsource the translation task to a professional translator and question of validating still remains because it is not necessary that a person who requested the documents to be translated knows the translated language. The early approach of machine translation was based on mapping sentence and using dictionary. However, grammar plays a huge roles in every language and can not be define with mathematical rules or logics, that was the key issue until late 19s, an emerging field of computer science - \acrfull{ml} was coming in focus, the algorithm like decision trees provided better grasp for machine to decide based on confidence derived from if-than logics providing optimal results and probabilities. The disruptive achievement of Apple (integration of a voice assistant "Siri") has change the perspective of the world towards \acrshort{nlp}. The assistance was not as capable as an experienced staff but it opened the doors for manufactures to improve the technology. Later, different companies started approaching various approaches and the field \acrshort{nlp} reached majority field from agriculture to medical field.

Currently, the shift  in \acrshort{ml} has changed to deep learning thanks to availability of a good computational power, computers can perform more complex tasks in fraction of seconds. That allowed \acrshort{nlp} models to be able to deal not just with text or audio but with visuals as well. With increasing reach of digitization, \acrfull{vdu} has acquired remarkable attention owing to the fact that approx 80\% of the document exits are not in machine readable format. In addition languages and layouts within the documents are making it difficult to perform \acrshort{vdu}. It is quite visionary to have access to a system that can perform Structure Document Understanding or \acrshort{vdu} correctly, since documents are being used in almost every field, Therefore the impact of Automatic Document Processing is bigger than it seems. Machine can not just read the document like humans, Before we perform \acrshort{vdu} on any document, we need to make sure that the document is in readable format for extracting text and there are number of amount of text-types for instance Handwritten, plain, text in Logos, Signature and so on. \acrshort{ocr} made possible to convert document or scanned images into editable and allows machine to read and process the text that allows to train the models on almost every type of documents that include texts. Transformers are being popular to perform \acrshort{vdu}. Transformers are able to enable machine to understand, interpret and generate human-like responses with higher accuracy. The term "Transformer" first appeared in groundbreaking paper "Attention Is All You Need" \cite{vaswani2017attention}. The paper presents a novel architecture to achieve sequence-to-sequence task with handling long-range dependency in sentences. 

Despite of having a quality computational power to run neural-nets faster, there are number of challenges to make use of these models at production level, that includes scaling and distributed computational system to perform task on a large number of requests. Introduction of cloud computing has changed the way of computation in terms of consistency and availability of the product and services. Centralized data security, High performance and availability, accessibility, scalability, virtual computing, Agility and many more are upper hand of the cloud technology. In addition, cloud are more sustainable and greener since it reduces the dependency on up front investment for resources in small scale companies and businesses. People or groups can easily share and work together via shared spaces. In the event of disaster or cyber attacks, some cloud technologies provide built in backups, helping businesses to recover faster. 

\section{Contributions and Thesis Outline}
This thesis includes some key concerns, challenges that should be discussed while developing \acrlong{ml} "as-a-service". The aim of this thesis is to make a software as a service that can process documents. That includes first to find a way to deal with the content of the documents. Second to find an infrastructure to build a software as a service. In upcoming chapters, the motivation behind choosing \acrshort{ml} to deal with language and layout inside documents will be described (\Cref{Chapter_Methods}) with some background of key concerns, challenges in the field of \acrshort{nlp} and some related work regarding these challenges (\Cref{Chapter_Background}). In addition, the traditional and relatively new ways of software deployment will be also discussed in order to find a suitable infrastructure that can be fast, scalable, cost-effective and secure to build, develop and deploy the \acrshort{ml} as-a-service (\Cref{Chapter_deployment}).  

 Our approach was to first find model and methodology that can be used for more than one languages since finding a model and methodology to deal with each languages differently costs time and resources. Having access to a general model and methodology that can be used for all languages will make it easier to build, develop and deploy in the future. Therefore, we decided to first build a prototype that can perform document content classification for one specific language (German) in order to have good performance in one language that can be deploy in \acrshort{saas} manner. Later on the model will be evaluated on the one specific language that it had been trained on and few other languages as well in order to find whether the model shows possibility of being multi-lingual \Cref{Chapter_Evaluation}. The datasets containing different language documents with statistics on dataset and the model performance on specific task is presented which can be used to train a proposed model for other available languages or future tasks. Last, the overview of deploying these model is presented that can be used for the proposed model and tasks, regardless of the language model has been trained, the deployment workflow can be implemented for proposed model that is scalabel, fast and cost effective to serve \acrlong{ml} models as \acrlong{saas} 



% This thesis includes the framework and functionality of the proposed model with a deployment on cloud platform and technologies. The model is used to classify the document content into four classes "Question, Answer, Header, Other". Model framework uses text and layout information and combine them to enhance the input features before carrying out classification in order to improve the predictions in the language other than the model is trained or fine-tuned on. In chapter "Background", the necessary terms have been explained to understand all the steps. In chapter "Methods", methods that defines the problem, similar approaches and my approach has been described. Chapter "Data-Preparation" gives information about the data set that has been used to fine tune the proposed model. 



%     It is quite visionary to have system that can perform \acrshort{vdu} task correctly. 


% technique for \acrshort{mt} was based on 

% Discussing of a Language, it is very broad and complex field, it can cost time and money. In recent years, machine translation has gain significant attention. 



%  Documents! It has numerous types, from handwritten to machine generated, that includes images, books, articles, newspapers, bills, pdfs, emails, posters, all kind of forms and so on. In addition all of them have different languages and layouts and roughly, more than 80 \% of documents exists are not in machine readable format. Documents are crucial part in Globalization, since internationalized company should provide their well translated documents for their products and services in order to be successful. Documents are being used in every steps and target groups, from designing to manufacturing, from logistics to shops, customer-satisfactions, functionality and security features of product and so on. Having a system that can perform \acrshort{vdu} correctly can help companies reduce their time and costs.

%  \acrlong{nlp} is a complex issue.

 